Nail: A practical interface generator for binary formats

### 2014-04-01 paper/intro.tex
one more par

A promising approach to avoid such vulnerabilities is to specify
a precise grammar for the input data format, and to build a tool for
parsing inputs given a particular grammar, such as the traditional {\tt
lex} and {\tt yacc} generators.  Applications that use such a tool to
process input data will not need to write error-prone input processing
code, and as long as the tool is bug-free, the application will be safe
from input processing vulnerabilities.

Working with generic tree structures is tiresome, so the programmer can
bind a \textit{semantic action} to a sub-parser. Whenever the sub-parser
is successfully invoked, the parser executes the semantic action on the
output of the sub-parser and places the result as a leaf node in the
syntax tree. Other parser generators frequently skip the AST entirely,
requiring the programmer to specify a semantic action with every rule
in the grammar.

Semantic actions are one source of vulnerability within automatically
generated parsers, as they are typically implemented in C or another
general purpose programming language and perform dangerous operations
such as memory allocation and copying. If there is a bug in the semantic
actions, the attacker is likely able to craft an input that invokes the
semantic actions with controllable inputs, as the inputs have not been
fully verified yet.

>>>>

A promising approach to avoid such vulnerabilities is to specify a
precise grammar for the input data format, and to use a parser generator,
such as {\tt lex} and {\tt yacc}, to synthesize the input processing
code.  Developers that use a parser generator will not need to write
error-prone input processing code on their own, and as long as the
parser generator is bug-free, the application will be safe from input
processing vulnerabilities.  Unfortunately, applying this approach in
practice, using state-of-the-art parser generators, requires addressing
several challenges.

First, parser generators typically parse inputs into an abstract syntax
tree (AST) that corresponds to the grammar.  In order to produce a data
structure that the rest of the application code can easily process,
application developers must write explicit {\em semantic actions} that
update the application's internal representation of the data based on
each AST node.  Writing these semantic actions by hand is error-prone,
much like other input processing code, and mistakes can result in memory
corruption bugs or misinterpreted inputs.
